---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(collapse  = TRUE,
                      comment   = "#>",
                      fig.path  = "man/figures/",
                      out.width = "100%")
```



## :mortar_board: Practice 5 - Renv


<!-- badges: start -->
[![License: GPL-2](https://img.shields.io/badge/License-GPL%20v2-blue.svg)](https://choosealicense.com/licenses/gpl-2.0/)
<!-- badges: end -->


Structure of the research compendium of the [practice 5](https://rdatatoolbox.github.io/ex-targets.html) of the training course 
[**Reproducible Research in Computational Ecology**](https://rdatatoolbox.github.io).



### Content

This repository is structured as follow:

- [`data/`](https://github.com/rdatatoolbox/practice5/tree/main/data):
contains all raw data required to perform analyses

- [`R/`](https://github.com/rdatatoolbox/practice5/tree/main/R):
contains R functions developed especially for this project

- [`DESCRIPTION`](https://github.com/rdatatoolbox/practice5/tree/main/DESCRIPTION):
contains project metadata (author, date, dependencies, etc.)

- [`_targets.R`](https://github.com/rdatatoolbox/practice5/tree/main/_targets.R):
contains the pipeline

- [`index.Rmd`](https://github.com/rdatatoolbox/practice5/tree/main/index.Rmd):
contains the final report to knit

- [`make.R`](https://github.com/rdatatoolbox/practice5/tree/main/make.R):
main R script to run the entire project by running `targets::tar_make()`



### Usage

- Fork and clone this repository
- Open a terminal
- Build the Docker image with:

```sh
docker build -t "practice5" .
```

- Start a container based on this image:

```sh
docker run --rm -dp 8787:8787 -e DISABLE_AUTH=true practice5
```

- On a web browser enter this URL: `127.0.0.1:8787`. A new RStudio Server
instance will be available.
- To run the analysis:

```{r eval = FALSE}
source("make.R")
```



### Notes

- All required packages, listed in the `DESCRIPTION` file, will be installed (if necessary)
- All required packages and R functions will be loaded



### How to cite

> Casajus N, Bonnici I, Dray S, Gimenez O, Guéry L, Guilhaumon F, Schiettekatte NMD & Siberchicot A (2023) Workshop FRB-CESAB & GdR EcoStat: Reproducible Research in Computational Ecology. Zenodo. <http://doi.org/10.5281/zenodo.4262978>.
